Technical Report

### 2024-02-29 Reports/tech_report1.tex
update report

>>>>

\section{February 28 experiments}

\subsection{Compute gamma for layer 9 for normal 5x100, pure y-constraints}

This experiment is to compute the gamma of layer 9 normal 5x100 with pure-y constraints constraints, with open 80 node.

The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|. And the partial output file name is \verb*|DL_V0p3_layer9_gamma_open_80.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 9 with open 80 ReLU.

\begin{itemize}
	\item\emph{Experiments Id}: 022800102024

	\item\emph{Open $\ReLU$ number:} Open 80 ReLU node

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_27_18_03_13.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method. 
\end{itemize}

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_layer9_gamma_open_80.txt|.

	\item \emph{Total time:} 36039.55334234238s.

	\item \emph{Key results:}  The average gamma of this layer is:  10.779673641817366

	The average solution for gamma of this layer is:  9.890623948009639

	\item  \emph{Binary output}: It does not generate a binary file. I do not know why.
